Combining Linked data and Data Mining Techniques to improve Clustering of Large Scale Media Repositories: A case study with BBC

### 2016-04-28 paper/paper.tex

@@

@@

\section{Analysis}

>>>>

\usepackage[dvipsnames]{xcolor}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{listings}
\DeclareCaptionFont{white}{ \color{white} }
\DeclareCaptionFormat{listing}{
  \colorbox[cmyk]{0.43, 0.35, 0.35,0.01 }{
    \parbox{\textwidth}{#1#2#3}
  }
}
\captionsetup[lstlisting]{ format=listing, labelfont=white, textfont=white, singlelinecheck=false, margin=0pt, font={bf,footnotesize} }

% Language Definitions for SPARQL
\lstdefinelanguage{sparql}{
morestring=[b][\color{blue}]\",
morekeywords={SELECT,CONSTRUCT,DESCRIBE,ASK,WHERE,FROM,NAMED,PREFIX,BASE,OPTIONAL,FILTER,GRAPH,LIMIT,OFFSET,SERVICE,UNION,EXISTS,NOT,BINDINGS,MINUS,a},
sensitive=true
}

\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily\footnotesize,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}

\lstset{frame=single,captionpos=b}

@@

An experiemental system was designed and built around the following
high-level requirements:

\begin{enumerate}
\item gathering (meta)data about all of an organisations content items;
\item further enriching that metadata with information not explicitly present
in the content item itself; and
\item applying machine learning to that content metadata to gain new insights
about that content.
\end{enumerate}

The system was also designed with the end goal of being able to present
users with alternative content items deemed similar to any given item they
are currently ready or watching. This provided a focus to ensure some
industrial application of the experiment and also a means by which to evaluate
the results in that results can be scored on how they perform at driving
such a website feature.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=\linewidth]{../report/diagrams/component.png}
  \end{center}
  \caption{High-level component diagram with interfaces for each use case\label{fig:component}}
\end{figure}

Figure~\ref{fig:component} shows a high-level view of a ``Content Miner''
software application. A set of ``notifier''
applications can be created to connect different content production and
management systems to the data mining system such that it is notified when new
content is created. The notification need only be an \emph{IRI} that uniquely
identifies that content item. Once the application has meaningful clusters of
content, we can imagine another system that can query this miner application
to provide some view of related content given some initial content item.

\subsection{Data Pipeline}

The overall content miner system conflates the two jobs of generating
feature sets suitable for data mining and also the data mining process itself.
Thus a core subsystem in the overall system is a conceptual data pipeline whose
input is a URI or IRI identifying a content item published on an organisation's
website and the output is feature sets ready for applying machine learning.

This subsystem was conceptually modelled as a data ``pipeline'' that takes
an IRI identifying a piece of web content at the source end and produces
feature sets at the other end. In this pipeline, the three primary data
structures employed are the \emph{IRI}\footnote{http://tools.ietf.org/html/rfc3987}
(in many cases the public URL for the content's primary page is sufficient),
the \emph{feature set} (modelled as a schema-less set of key-value pairs)
and the \emph{RDF graph} as an intermediate structure for manipulating along
the pipeline.

The data pipeline was then designed inductively, introducing potential
methods for creating RDF graphs from web content and also enriching those
graphs.

\begin{centering}
\begin{lstlisting}[label=lst:jsonld-identity,caption={Identity graph for a content item in JSON-LD syntax},language=json]
{
  "@id": "http://example.com/entity/1",
  "@graph": []
}
\end{lstlisting}
\end{centering}

With the knowledge only of a content item's IRI, we are arguably only able to
produce an empty named RDF graph. Such a graph for an example IRI
\texttt{http://example.com/entity/} is illustrated in
JSON-LD syntax in Listings~\ref{lst:jsonld-identity}. This provides our
base case in the inductive design.

Paulheim and F\"urnkranz\cite{paulheim2012unsupervised} described a number of
SPARQL queries for generating feature sets from RDF data, inspired
a simple query such as that shown in Listings~\ref{lst:simple-sparql}. This
query generates a boolean \texttt{true} value for any properties that match
and implies \texttt{false} for those that do not and we then flatten this into
a simple feature format: \texttt{?p\_?o=true},
e.g. \texttt{rdf:type\_schema:Article=true}

\begin{lstlisting}[label=lst:simple-sparql,caption={Generates field \texttt{content\_?p\_?v} with value \texttt{true}},language=sparql]
SELECT ?p ?o
WHERE { ?iri ?p ?o . }
FILTER isIRI(?o)
\end{lstlisting}

Note that this ignores triples whose objects are literals, for which case the
a analogous strategy as shown in listings~\ref{literal-sparql} was employed to
produce features of the form: \texttt{?p=?v}.

\begin{lstlisting}[label=lst:literal-sparql,caption={Generates field \texttt{content\_?p\_?v} with value \texttt{true}},language=sparql]
SELECT ?p ?v
WHERE { ?iri ?p ?v . }
FILTER isLiteral(?o)
\end{lstlisting}

Finally, an additional layer of indirection was created

@@

\section{Analysis and Evalaution}
